An improved platform for Web service wrapping, discovery and consumption

### 2010-06-14 trunk/papers/icsoc2010/paper_sec_use_case.tex
minor change
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@847 d8b0c59b-6544-0410-94d9-83a5658a058e

The two artifacts presented in this paper may be deployed and used separately by third-party applications. The intention was to show the advances made regarding web service discovery and consumption. However, they were developed in order to be part of the FAST platform. FAST constitutes a novel approach to application composition and business process definition from a top-down user-centric perspective. Therefore, it is aimed to allow users to create their own applications by combining different components, or building blocks, such as graphical forms and back-end services in terms of their inputs and outputs. These two components, as described in Section 3 and 4, are fully integrated and present a high cohesion the rest of the components of the FAST architecture (see Picture \ref{pic:fast_architecture}.

>>>>

The two artifacts presented in this paper may be deployed and used separately by third-party applications. The intention was to show the advances made regarding web service discovery and consumption. However, they were developed in order to be part of the FAST platform. FAST constitutes a novel approach to application composition and business process definition from a top-down user-centric perspective. Therefore, it is aimed to allow users to create their own applications by combining different components, or building blocks, such as graphical forms and back-end services in terms of their inputs and outputs. These two components, as described in Section 3 and 4, are fully integrated and present a high cohesion the rest of the components of the FAST architecture (see Picture~\ref{pic:fast_architecture}.
